### 2018-07-04 paper/4-build.tex
Revise S4.1.2 Restarting

The topological scheduler has two downsides: it is limited to \hs{Applicative}
build systems and requires a fresh topological sort each time. \simon{If the tasks don't change,
  the dependencies are unchanged, so the topological sort from the last time
  will do fine, won't it?}  So, while the
actions themselves may be incremental (i.e. unnecessary tasks will not be
performed), the pre-processing is not. We can incrementalise the topological
sort by storing the topological order between build runs, using it as a starting
point in the next run, fixing it up if the build discovers any inconsistency, as
\Excel does.

This approach requires a way to abort tasks that have failed due to out-of-date
dependencies. It is also not minimal in the sense that a task may start, do some
meaningful work, and then abort. However, in the case of an \hs{Applicative}
system, that work is zero.

\Bazel's restarting scheduler does not store the topological order between build
runs; instead, it stores the most recent task dependency information. Since this
information may become outdated, \Bazel may also need to abort a task if a
newly discovered dependency is out-of-date.

>>>>

To handle dynamic dependencies we can use the following speculative approach:
build tasks in an arbitrary order, discovering their dependencies on the fly;
whenever a task calls \hs{fetch} on an out-of-date key \hs{dep}, abort the task,
and switch to building the dependency \hs{dep}; eventually the previously
aborted task is restarted and makes further progress thanks to \hs{dep} now
being up to date. When a build completes, we can record the resulting order,
using it as a starting point for the next build and fixing it up if a task's
dependencies have changed, as \Excel does.

This approach requires a way to abort tasks that have failed due to out-of-date
dependencies. It is also not minimal in the sense that a task may start, do some
meaningful work, and then abort.

\Bazel's restarting scheduler does not store the discovered order between build
runs; instead, it stores the most recent task dependency information. Since this
information may become outdated, \Bazel may also need to abort a task if a
newly discovered dependency is out-of-date.
